Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-01-18 manuscript.tex
Spellcheck run [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/a18ba04b97dde37819acb8fe14c660c56a246eac.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/a18ba04b97dde37819acb8fe14c660c56a246eac/checks
https://github.com/habi/acinar-analysis-manuscript/runs/494015869

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681} and is under revision in the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...ca2252149052d2112e9155e62f10bf5e05075b68}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/ca2252149052d2112e9155e62f10bf5e05075b68/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/ca2252149052d2112e9155e62f10bf5e05075b68}{habi/acinar-analysis-manuscript@ca22521}
on January 18, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(ca22521)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(ca22521)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Switzerland
\end{itemize}

@@

However, relative numbers as reported in this study are more reliable.
This is especially the case when the comparison is done in groups of animals processed in parallel and counted by the same operator.
We assessed the same lungs as Tschanz et al.~(\protect\hyperlink{ref-wnl86DEM}{46}), but performed our assessement based on a very different imaging method and with two different persons performing the stereological assessment at two very different points in time.
Furthermore, we used the number of acini as determined by Barre et al.~(\protect\hyperlink{ref-uFNlWogb}{3}) which represents a dataset obtained by a third team and which introduces the effect of error propagation.
This may explain the relative factor of 5.04 that we found as a difference.
Even if it was shown that the right lower lobe represents a valid sample for the entire lung (\protect\hyperlink{ref-14OP85b2F}{2}, \protect\hyperlink{ref-I9TmP6IU}{53}), we cannot rule out a contribution to the factor by regional differences in the lung which we can not account for in the present study.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681} and is under revision in the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...a18ba04b97dde37819acb8fe14c660c56a246eac}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/a18ba04b97dde37819acb8fe14c660c56a246eac/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/a18ba04b97dde37819acb8fe14c660c56a246eac}{habi/acinar-analysis-manuscript@a18ba04}
on January 18, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(a18ba04)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(a18ba04)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Switzerland
\end{itemize}

@@

However, relative numbers as reported in this study are more reliable.
This is especially the case when the comparison is done in groups of animals processed in parallel and counted by the same operator.
We assessed the same lungs as Tschanz et al.~(\protect\hyperlink{ref-wnl86DEM}{46}), but performed our assessment based on a very different imaging method and with two different persons performing the stereological assessment at two very different points in time.
Furthermore, we used the number of acini as determined by Barre et al.~(\protect\hyperlink{ref-uFNlWogb}{3}) which represents a dataset obtained by a third team and which introduces the effect of error propagation.
This may explain the relative factor of 5.04 that we found as a difference.
Even if it was shown that the right lower lobe represents a valid sample for the entire lung (\protect\hyperlink{ref-14OP85b2F}{2}, \protect\hyperlink{ref-I9TmP6IU}{53}), we cannot rule out a contribution to the factor by regional differences in the lung which we can not account for in the present study.
